---
title: "MyFirstPackage Vignette"
author: "YHu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Here is the vignette of my first package. 

# What the Package is About
The package contains several function to read and proces data from the *Fatality Analysi Reporting System*. Below is a list of the functions:

|Function Name         |Description                                         |
|----------------------|----------------------------------------------------|
|fars_read|Read data from a csv file. The function also uses the tbl_df wrapper from dplyr to make sure the system won't print a lot of data to the screen.|
|make_filename|Make a file name with speicified accident year.|
|fars_read_years|Read user specified year for the FARS data|
|fars_summarize_years|Summarize number of accidents across each month for the specified year.|
|fars_map_state|Mapping the location of the accidents (based on latitude and longitude) with user speicifed state numbe and accident year|

# How to use 
This section provides the example code to use the functions included in this package.

##fars_read()
```{r,eval=FALSE}
data <- fars_read("accident_2013.csv.bz2")
```
##make_filename()
```{r,eval=FALSE}
make_filename(2013)
```
##fars_read_years()
```{r,eval=FALSE}
fars_read_years(2013)
```
##fars_summarize_year()
```{r,eval=FALSE}
fars_summarize_years(2013)
```
##fars_map_state()
```{r,eval=FALSE}
fars_map_state(10,2013)
```
